Up to 25\% of beneficial mutations in protein sequences are not adaptive innovations in mammals

### 2022-11-29 manuscript/supp-mat.tex
Refactored manuscript

    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{5}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

    \newpage
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

    \newpage
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1 ]$ & $\frac{\mathbb{P}[\Sphy > 1]}{\mathbb{P}[ \Spop > 1 ]}$ & $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ & $\mathbb{P}[\Sphy > 1\given \Spop > 1 ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

@@

    \section{Mutation-selection models: histograms and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
    For each population, the same figure is shown.
    \begin{itemize}
        \item Top-left panel: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red).
        \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
        At high frequencies, supposedly severally deleterious mutations are underrepresented.
        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
    \end{itemize}

>>>>

    \subsubsection{$\dnds$ and beneficial back-mutations}
    \begin{center}
        \captionof{table}{$\dnds$ of beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{5}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

    \newpage
    \begin{center}
        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

    \subsubsection{Probabilities of beneficial back-mutations}
    \begin{center}
        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones with PolyDFE model C.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1 ]$ & $\frac{\mathbb{P}[\Sphy > 1]}{\mathbb{P}[ \Spop > 1 ]}$ & $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ & $\mathbb{P}[\Sphy > 1\given \Spop > 1 ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.

    \newpage
    \begin{center}
        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model C.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [ \Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[ \Spop > 0 ]}$ & $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0\given \Spop > 0 ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot
            Equus c. &      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.125$ &                                     $ 0.403$ &                       $ 1.000$ &                 $ 0.403$ \\
            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.108$ &                                     $ 0.457$ &                       $ 0.640$ &                 $ 0.293$ \\
            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.104$ &                                     $ 0.477$ &                       $ 0.708$ &                 $ 0.338$ \\
            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.471$ &                       $ 0.416$ &                 $ 0.196$ \\
            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.102$ &                                     $ 0.495$ &                       $ 0.464$ &                 $ 0.230$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.473$ &                       $ 0.327$ &                 $ 0.155$ \\
            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.089$ &                                     $ 0.569$ &                       $ 0.384$ &                 $ 0.219$ \\
            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.096$ &                                     $ 0.525$ &                       $ 0.402$ &                 $ 0.211$ \\
            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.088$ &                                     $ 0.571$ &                       $ 0.408$ &                 $ 0.233$ \\
            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.066$ &                                     $ 0.769$ &                       $ 0.159$ &                 $ 0.122$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.074$ &                                     $ 0.686$ &                       $ 0.259$ &                 $ 0.177$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.084$ &                                     $ 0.605$ &                       $ 0.499$ &                 $ 0.302$ \\
            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.071$ &                                     $ 0.712$ &                       $ 0.253$ &                 $ 0.180$ \\
            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.060$ &                                     $ 0.839$ &                       $ 0.155$ &                 $ 0.130$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.121$ &                                     $ 0.392$ &                       $ 0.771$ &                 $ 0.303$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.105$ &                                     $ 0.454$ &                       $ 0.637$ &                 $ 0.289$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.120$ &                                     $ 0.395$ &                       $ 0.708$ &                 $ 0.280$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.090$ &                                     $ 0.528$ &                       $ 0.725$ &                 $ 0.383$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.106$ &                                     $ 0.447$ &                       $ 0.627$ &                 $ 0.280$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.111$ &                                     $ 0.429$ &                       $ 0.676$ &                 $ 0.290$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.104$ &                                     $ 0.456$ &                       $ 0.659$ &                 $ 0.301$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.117$ &                                     $ 0.405$ &                       $ 0.723$ &                 $ 0.293$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.116$ &                                     $ 0.409$ &                       $ 0.671$ &                 $ 0.275$ \\
            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.114$ &                                     $ 0.424$ &                       $ 1.000$ &                 $ 0.424$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.110$ &                                     $ 0.437$ &                       $ 1.000$ &                 $ 0.437$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.453$ &                       $ 1.000$ &                 $ 0.453$ \\
            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.107$ &                                     $ 0.452$ &                       $ 1.000$ &                 $ 0.452$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.454$ &                       $ 1.000$ &                 $ 0.454$ \\
        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation a beneficial back-mutation.
        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy > 0$), thus toward a more fit amino-acid.
        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be beneficial.
        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop > 0$), estimated from all SNPs in the population.
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop > 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.

    \newpage
    \begin{center}
        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model D.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy \geq 0]$ & $\mathbb{P} [ \Spop \geq 0 ]$ & $\frac{\mathbb{P}[\Sphy \geq 0]}{\mathbb{P}[ \Spop \geq 0 ]}$ & $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ & $\mathbb{P}[\Sphy \geq 0\given \Spop \geq 0 ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot
            Equus c. &      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.219$ &                                     $ 0.230$ &                       $ 0.461$ &                 $ 0.106$ \\
            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.181$ &                                     $ 0.274$ &                       $ 0.407$ &                 $ 0.112$ \\
            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.175$ &                                     $ 0.283$ &                       $ 0.470$ &                 $ 0.133$ \\
            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.182$ &                                     $ 0.277$ &                       $ 0.472$ &                 $ 0.131$ \\
            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.177$ &                                     $ 0.286$ &                       $ 0.492$ &                 $ 0.141$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.171$ &                                     $ 0.295$ &                       $ 0.463$ &                 $ 0.137$ \\
            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.161$ &                                     $ 0.313$ &                       $ 0.450$ &                 $ 0.141$ \\
            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.174$ &                                     $ 0.291$ &                       $ 0.509$ &                 $ 0.148$ \\
            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.170$ &                                     $ 0.298$ &                       $ 0.442$ &                 $ 0.132$ \\
            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.141$ &                                     $ 0.359$ &                       $ 0.506$ &                 $ 0.182$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.365$ &                       $ 0.484$ &                 $ 0.177$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.134$ &                                     $ 0.379$ &                       $ 0.517$ &                 $ 0.196$ \\
            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.136$ &                                     $ 0.372$ &                       $ 0.513$ &                 $ 0.191$ \\
            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.364$ &                       $ 0.477$ &                 $ 0.174$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.205$ &                                     $ 0.232$ &                       $ 0.543$ &                 $ 0.126$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.345$ &                 $ 0.091$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.464$ &                 $ 0.108$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.183$ &                                     $ 0.260$ &                       $ 0.442$ &                 $ 0.115$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.478$ &                 $ 0.127$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.552$ &                 $ 0.129$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.184$ &                                     $ 0.258$ &                       $ 0.477$ &                 $ 0.123$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.204$ &                                     $ 0.233$ &                       $ 0.527$ &                 $ 0.123$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.187$ &                                     $ 0.253$ &                       $ 0.477$ &                 $ 0.121$ \\
            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.239$ &                                     $ 0.202$ &                       $ 0.158$ &                 $ 0.032$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.252$ &                                     $ 0.192$ &                       $ 0.452$ &                 $ 0.087$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.260$ &                                     $ 0.185$ &                       $ 0.440$ &                 $ 0.082$ \\
            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.255$ &                                     $ 0.189$ &                       $ 0.453$ &                 $ 0.086$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.248$ &                                     $ 0.194$ &                       $ 0.439$ &                 $ 0.085$ \\
        \item $\mathbb{P} [ \Sphy \geq 0 ]$ is the probability for a new mutation a beneficial back-mutation.
        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy \geq 0$), thus toward a more fit amino-acid.
        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
        \item $\mathbb{P} [ \Spop \geq 0 ]$ is the probability for a mutation to be beneficial.
        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop \geq 0$), estimated from all SNPs in the population.
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
        \item $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop \geq 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy \geq 0$).
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
        \item $\mathbb{P} [ \Sphy \geq 0 \given \Spop \geq 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories, where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
    We used $K=5$ with $\Spop_1 = -400$, $\Spop_2 = -10$, $\Spop_3 = 0$, $\Spop_4 = 1$, $\Spop_5 = 4$.\\

    Altogether, comparing tables S3-S5, we acknowledge that estimating the proportion of beneficial back-mutations among all beneficial ones is dependent on the assumption for the underlying distribution of fitness effects at the population scale and the threshold used to define a beneficial mutation.
    \newpage

@@

    \section{Distribution of fitness effects}

    \captionof{figure}{~}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
    \end{minipage}
    \begin{itemize}
        \item Left panel: Distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
        \item Middle panel: Distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}).
    \end{itemize}
    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.

    \section{Mutation-selection models: DFE and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
    For each population, the same figure is shown.
    \begin{itemize}
        \item Top-left panel: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
        Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
        \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
        At high frequencies, supposedly severally deleterious mutations are underrepresented.
        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
    \end{itemize}
